\documentclass[12pt]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{hyperref} % for web addresses
\usepackage{url} % for file paths

\usepackage{mathptmx}

\usepackage{parskip}

\usepackage{natbib}
\bibliographystyle{abbrvnat}
%\setcitestyle{authoryear,open={((},close={))}}
\setcitestyle{super}

\usepackage[strings]{underscore}

\newcommand{\ruediPy}{\texttt{ruediPy}}

\newcommand{\work}[1]{{\Large\bf\ensuremath{\star}}\footnote{TO DO: #1}}

\title{\ruediPy\ documentation}
\author{Matthias Brennwald}
\date{Version \today}							% Activate to display a given date or no date

\begin{document}

\maketitle

\begin{abstract}
\ruediPy\ is a collection of Python programs for instrument control and data acquisition using RUEDI instruments \citep{Brennwald:2016a}. \ruediPy\ also includes some GNU Octave (or Matlab) tools to load, process, and manipulate RUEDI data acquired with \ruediPy\ Python classes.\par

\ruediPy\ is distributed as free software under the GNU General Public License (see LICENSE.txt).

This document describes the \ruediPy\ software only. The RUEDI instrument is described in a separate document\citep{Brennwald:2016a}.


\end{abstract}

\tableofcontents

\clearpage

\section{Overview}
\ruediPy\ is a collection of Python programs for instrument control and data acquisition using RUEDI instruments. \ruediPy\ also includes some GNU Octave (or Matlab) tools to load, process, and manipulate RUEDI data acquired with \ruediPy\ Python classes. The RUEDI instrument itself is described in a separate document\citep{Brennwald:2016a}.\par

The Python classes for instrument control and data acquisition are designed to reflect the different hardware units of a RUEDI instrument, such as the mass spectrometer, selector valve, or probes for total gas pressure or temperature. These classes, combined with additional helper classes (e.g., for data file handling), allow writing simple Python scripts that perform user-defined procedures for a specific analysis task.\par

The GNU Octave tools (m-files) are designed to work hand-in-hand with the data files produced by the data acquisition parts of the Python classes. \work{expand this: load raw data, process / calibrate data, etc.}

\ruediPy\ is developed on Linux and Mac OS X systems, but should also work on any other system that runs Python and GNU Octave. \ruediPy\ has been reported to (partially) work on Windows. Linux is the recommended choice and is assumed throughout this manual. Python 3.0 or newer is required.\par

\section{Obtaining and installing \ruediPy}
\ruediPy\ can be downloaded from \url{http://brennmat.github.io/ruediPy} either as a compressed archive file, or using Subversion or Git version control systems. \ruediPy\ can be installed to just about any directory on the computer that is used for instrument control -- but the user home directory  (\path{~/ruediPy}) may seem like a sensible choice, and that's what is assumed throughout the examples shown in this manual.

As an example, here's a step-by-step list of terminal commands to install \ruediPy  on a Linux computer running Ubuntu 16.04. Other Linux distributions will be similar. The user account name in this example is ``\texttt{mRdemo}'', and this user account is enabled for \texttt{sudo} operations (i.e., it has `admin' rights):
\begin{enumerate}

\item Update system software to latest versions and install basic software requirements for \ruediPy:\par
\texttt{sudo apt-get update}\\
\texttt{sudo apt-get upgrade}\\
\texttt{sudo apt-get install octave subversion python3-pip}\\
\texttt{sudo apt-get install python3-serial python3-matplotlib python3-scipy python3-termcolor}\\
\texttt{sudo -H pip3 install pydigitemp pynput}\\

\item Download ruediPy:\par
\texttt{svn co https://github.com/brennmat/ruediPy.git/trunk \path{~/ruediPy}}


\item Set permission to access the serial ports:\par
\texttt{sudo usermod -a -G dialout mRdemo}

\item Prepare directories for \ruediPy\ data files and your measurement scripts:\par
\texttt{mkdir \path{~/data}}\\
\texttt{mkdir \path{~/scripts}}

\item \emph{Optional:} If you intend to run your own custom Python scripts, you may need to set the Shell and Python searchpaths. To this end, you may want to configure the paths using a dedicated file in your home directory (e.g., \path{ruediPy_paths.txt}). Execute the following terminal commands to set up this file and the searchpaths (copy and paste to the Terminal prompt should work):\par
{\scriptsize
\mbox{\texttt{echo PROJECT_SCRIPTS=\path{~/scripts/my_project_scripts} >> \path{~/ruediPy_paths.txt}}}\\[-1.5ex]
\mbox{\texttt{echo export PYTHONPATH=\path{~/ruediPy/python} >> \path{~/ruediPy_paths.txt}}}\\[-1.5ex]
\mbox{\texttt{echo export PYTHONPATH=\textsc{\char13}\$PYTHONPATH\textsc{\char13}:\textsc{\char13}\$PROJECT_SCRIPTS\textsc{\char13} >> \path{~/ruediPy_paths.txt}}}\\[-1.5ex]
\mbox{\texttt{echo export PATH=\textsc{\char13}\$PATH\textsc{\char13}:\textsc{\char13}\$PROJECT_SCRIPTS\textsc{\char13} >> \path{~/ruediPy_paths.txt}}}\\[-1.5ex]
\mbox{\texttt{echo source \textsc{\char13}\$HOME\textsc{\char13}\path{/ruediPy_paths.txt} >> \path{~/.profile}}}
}

Adjust the \texttt{PROJECT_SCRIPTS} setting in the \path{ruediPy_paths.txt} file to reflect the directory where your measurement scripts are (or will be) stored. It is recommended to keep measurement scripts for different analyis types or different projects in dedicated directories. Changing from one analysis type (or project) to another is achieved by adjusting \texttt{PROJECT_SCRIPTS} in the \path{ruediPy_paths.txt} file accordingly.

\end{enumerate}

You should also consider setting up the computer to avoid going to `sleep' mode, because this might interrupt the measurement procedure. You may also want to turn off `sleep' mode when the laptop lid is closed (with the Gnome-3 desktop enviornment, use Gnome Tweak Tool to turn this off).\par

%{\scriptsize
%\mbox{\texttt{gsettings set org.gnome.settings-daemon.plugins.power lid-close-ac-action \textsc{\char13}nothing\textsc{\char13}}}\\
%\mbox{\texttt{gsettings set org.gnome.settings-daemon.plugins.power lid-close-battery-action \textsc{\char13}nothing\textsc{\char13}}}
%}

\enlargethispage{2\baselineskip}

Finally, it may be useful to increase the size of the cursor if it's hard to see on the screen during poor light conditions during field work. This can be achieved using the following command (for the GNOME desktop environment):\par
\mbox{\texttt{dconf write /org/gnome/desktop/interface/cursor-size 64}}

Restart the computer to make the above changes active.\par


\section{Python classes}
\subsection{Overview}
The Python classes are used to control the various hardware units of the RUEDI instruments, to acquire measurement data, and to write these data to well-formatted and structured data files.\par

Currently, the following classes are implemented:
\begin{itemize}
\item \texttt{rgams\_SRS.py}: control and data acquisition from the SRS mass spectrometer
\item \texttt{selectorvalve\_VICI.py}: control of the VICI inlet valve
\item \texttt{pressuresensor\_WIKA.py}: control and data acquisition from the WIKA pressure sensor
\item \texttt{pressuresensor\_OMEGA.py}: control and data acquisition from the OMEGA pressure sensor
\item \texttt{datafile.py}: data file handling
\item \texttt{misc.py}: helper functions
\end{itemize}


The Python class files are located at \path{~/ruediPy/python/classes/}. To make sure Python knows where to find the \ruediPy\ Python classes, set your \texttt{PYTHONPATH} environment variable accordingly. A convenient method to achieve this on Linux or similar UNIXy systems is to put the following line to the \texttt{.profile} file: 
 \texttt{export PYTHONPATH=\path{~/ruediPy/python}}

These classes are continuously expanded and new classes are added to \ruediPy\ as required by new needs or developments of the RUEDI instruments. The various methods / functions included are documented in the class files. Due to the ongoing development of the code, it seems futile to keep an up-to-date copy of the methods / functions documentation in this manual. Please refer to the detailed documentation in the class files directly.

\subsection{Python classes reference}
\input{python_API.tex}

\section{GNU Octave tools}
The Octave tools (m-files) are located at \path{~/ruediPy/octave}. To make sure Octave knows where to find the \ruediPy\ Octave tools, set your Octave search path accordingly. A convenient method to achieve this is to include the corresponding \texttt{addpath(...)} commands in your \texttt{.octaverc} file.

The documentation and usage examples for the different \ruediPy\ Octave tools is available via the Octave \texttt{help} command.

\bibliography{ruediPyLit}

\end{document}  
\grid
\grid
